\Large\textbf{Decentralized Data Marketplace to Enable Trusted Machine Economy}

### 2019-10-26 paper.tex
Tweak related work

A 3-tier decentralized data marketplace architectural design\cite{3tierDataMarket} is known to reduce the burden of low-level devices, along with Ethereum smart contracts which consist of providers, consumers and brokers. The broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers. However, the data integrity and authentication of each participant is still forthcoming.

The sustainability of IoT economic system was under discussion by Dusit Niyato et al.\cite{UtilityStruct}. They evaluated the utility structure of data trading and presented game theory model.  Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found by game theory and the utility structure. However, refund and subscription mechanism were not mentioned in their work.

\section{\normalsize\textbf{System Architecture}}
Our proposed data marketplace framework is a 3-tier decentralized architecture with registrars, data providers, data consumers and brokers.

>>>>

A 3-tier decentralized data marketplace architectural design\cite{3tierDataMarket} is known to reduce the burden of low-level devices, along with Ethereum smart contracts to interact with providers, consumers and brokers. The broker is a trustless and highly resourced device that will facilitate the trading of data between the consumer and providers. However, the data integrity and authentication of each participant is still forthcoming.

The sustainability of IoT economic system was discussed by Dusit Niyato et al.\cite{UtilityStruct}. They evaluated the utility structure of data trading and presented game theory model.  Data marketplace organizers can determine their policies to ensure a sustainable system with the Nash Equilibrium found by game theory and the utility structure. However, refund and subscription mechanism were not mentioned in the original work.

\section{\normalsize\textbf{System Architecture}}
Our proposed data marketplace framework is a 3-tier decentralized architecture with a registrar who is responsible for marketplace registration in order to post participants' information on distributed ledgers for validation, data providers who publish data, data consumers who search for interested products and issue a new trade, and brokers who interact between data providers and consumers, including data publishing, product metadata generation and trading process.  Data integrity is enforced with the root of trust built on top of distributed ledgers for transparency and traceability.
